Searching 21-cm Absorption Systems in Chinese Radio Telescopes

### 2016-11-17 ms_21cm.tex
abstract

\abstract{
\keywords{}
}

@@

\section{Introduction}

FAST \citep{2016RaSc...51.1060L} and Tianlai \citep{2012IJMPS..12..256C}. Direct measurement of cosmic acceleration
\citep{2012ApJ...761L..26D}, and its proposal
on CHIME \citep{2014PhRvL.113d1303Y}

Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.

@@

>>>>

\abstract{
Neutral hydrogen clouds are known to exist in the Universe, however their spatial
distributions and physical properties are poorly understood. Such missing information
can be studied by the Chinese new generation radio telescopes by a blind searching
of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
systems by two representative radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST) and
Tianlai. The result shows that, in a few of years term,
these telescopes with either high sensitivity (FAST)
or wide field of view (Tianlai) can discover orders of magnitudes
more 21-cm absorption systems, than the cumulative discoveries
in the past 50 years. 
\keywords{}
}

@@

\section{Introduction}
21-cm absorption systems can be used to directly measure the cosmic acceleration
via Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
The current best constraint of this acceleration if given by 
\cite{2012ApJ...761L..26D}. A proposal
on CHIME-like telescope is given by \cite{2014PhRvL.113d1303Y},
in which the minor redshift drift could be measured over decades.
The uncertainties are from the poorly understood neutral hydrogen
clouds. Path finder surveys, taking less than a year, are needed
to improve our understandings of spatial distribution and physical
properties of neutral hydrogen clouds.
This can be done by the Chinese new generation radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST)
\citep{2016RaSc...51.1060L} and
Tianlai \citep{2012IJMPS..12..256C}.

\section{Sensitivity}

@@

\section{FAST estimation}

Parameters:

Result: 90 per month.

\section{Tianlai estimation}

Parameters:

Result: 80 per year.

\section{Conclusion}
